\documentclass{beamer}

\usepackage{datetime}
\usepackage{hyperref}

\newdate{today}{27}{9}{2021}

\title{ExCode Week 1}
\institute{University of Exeter}
\date{\displaydate{today}}

\begin{document}

\frame{\titlepage}

\begin{frame}
	\frametitle{About the Course}

	\begin{itemize}
		\item{Every DAY for 8 weeks (excluding reading
			week).}
		\item{18:30 to 19:00 - Lecture in the LECTURE THEATRE.}
		\item{19:00 to 19:30 - Practical in ROOM.}
		\item{Learn to program - not just Python!}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{About the People}

	\begin{itemize}
		\item{PERSON - Organises ExCode.}
		\item{PERSON - Delivers the lectures.}
		\item{Me - Teaching assistant, supervises practicals.}
	\end{itemize}

	I should be your first point of contact (email or WhatsApp). My email
	is \url{EMAIL}.

	If you have any issues with attendance contact PERSON
	(\url{EMAIL}.)
\end{frame}

\begin{frame}
	\frametitle{Required Material}

	\begin{itemize}
		\item{A laptop.}
		\item{A Google Account.}
		\item{Some space on your device.}
		\item{An internet connection.}
	\end{itemize}

	And most importantly, a willingness to learn! :D
\end{frame}

\begin{frame}
	\frametitle{Solutions}

	\begin{itemize}
		\item{Solutions to last week's exercise will be
			emailed out every DAY and discussed the next
			week.}
		\item{Don't worry if your solutions aren't exactly
			the same!}
		\item{If you have any issues, please feel free to contact
			me (email or WhatsApp group).}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Extracurricular}
	
	\begin{itemize}
		\item{Further reading - Think Python Book, W3Schools,
			Python documentation/tutorial.}
		\item{Try to practice on your own!}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Other Information}

	\begin{itemize}
		\item{Missing weeks.}
		\item{Google Colab.}
		\item{Changing groups/rooms.}
		\item{Health and safety.}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Focus}

	\begin{itemize}
		\item{Introduction to Python.}
		\item{Basic calculations.}
		\item{Showing things on the screen.}
	\end{itemize}
\end{frame}

\end{document}
